Farley et al. 2024

### 2025-01-10 IndividualStudies/AT_2025.qmd
added checkboxes to table

filter_select(id = "LipidProbe",
				label = "Functional probe used in pulldown:", 
				sharedData = AT_2025_Long_reactive,
				group = ~LipidProbe)

filter_select(id = "hit_annotation",
				label = "Enrichment criteria:", 
				sharedData = AT_2025_Long_reactive,
				group = ~hit_annotation)

>>>>

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = AT_2025_Long_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = AT_2025_Long_reactive,
                  group = ~hit_annotation)
)

### 2025-01-10 IndividualStudies/SF_2024.qmd
added checkboxes to table

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)

@@

filter_select(id = "LipidProbe",
				label = "Functional probe used in pulldown:", 
				sharedData = SF_2024_data_reactive,
				group = ~LipidProbe)

filter_select(id = "hit_annotation",
				label = "Enrichment criteria:", 
				sharedData = SF_2024_data_reactive,
				group = ~hit_annotation)

>>>>

```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)

@@

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = SF_2024_data_reactive,
                  group = ~hit_annotation)
)
